Linear stability analysis for \textit{monami} in a submerged sea grass bed

### 2015-09-17 ArXiV/grass.tex
Update ArXiV copy

%\documentclass[aps,prl,reprint,twocolumn,superscriptaddress,sort&compress,10pt]{revtex4-1}  % for review and submission
% \documentclass[aps,preprint,12pt]{revtex4-1}  % for review and submission
%\documentclass[aps,twocolumn,floatfix,prl,10pt]{revtex4-1}
%\documentclass[letterpaper,10pt,prl,twocolumn,aps]{revtex4-1}
%\documentclass[aps,preprint,floatfix,prl]{revtex4-1}
\documentclass{jfm}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{color}
\usepackage{longtable}
\usepackage{array}
\usepackage{amssymb}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}

\graphicspath{ {../Paper/images/}{../Paper/images/Growth_Rate_Cont_Plots/} }
\newcommand{\bx}{{\boldsymbol{\hat{x}}}}
\newcommand{\bn}{{\boldsymbol{\hat{n}}}}
\newcommand{\bt}{{\boldsymbol{\hat{t}}}}
\newcommand{\bu}{\mathbf{u}}
\newcommand{\grad}{\mathbf{\nabla}}
\newcommand{\del}{\partial}
\newcommand{\hg}{h_g}
\renewcommand{\Rey}{{R}}
\newcommand{\Ndg}{\tilde{N}_g}
\newcommand{\monami}{\textit{monami}}
\newcommand{\ubl}{U_\text{bl}}
\newcommand{\words}[1]{\textbf{(#1)~}}
% \newcommand{\words}[1]{{}}

@@

\definecolor{tableShade}{gray}{0.8}
% \title{\textit{Monami} as an oscillatory hydrodynamic instability in a submerged sea grass bed}
\title{Linear stability analysis for \textit{monami} in a submerged sea grass bed}
\author{
Ravi Singh\aff{1}, 
M. M. Bandi\aff{2},
Amala Mahadevan\aff{3}
\and
Shreyas Mandre\aff{4}}
\affiliation{
\aff{1}Department of Physics, Brown University, Providence RI 02912 USA
\aff{2}OIST Graduate University, Okinawa 904-0495, Japan
\aff{3}Woods Hole Oceanographic Institution, Woods Hole MA 02543 USA
\aff{4}School of Engineering, Brown University, Providence RI 02912 USA
}

\begin{document}
\maketitle

@@

% Chen and Jirka (1997), White and Nepf (2007). What are their results and how do they relate to ours? These analyses have investigated instability of hyperbolic tangent profiles using modified versions of Orr Sommerfeld or Rayleigh's equations in the context of shallow water flow instabilities. They have represented the additional drag arising due to vegetation or bottom friction using a parametrization analogous to ours. 
A modified version of the Orr-Sommerfeld equation was analyzed previously by \cite{Chu91}, \cite{Chen97}, and \cite{White07} in the context of instabilities in depth-averaged shallow water flows, where bottom friction replaces or augments vegetation drag.
They assumed the steady profile to be a hyperbolic tangent, the drag to be isotropic, and the flow domain to be infinite in $y$.
\cite{White07} also neglected the eddy viscosity in their stability analysis.
While a detailed investigation needed to compare the consequence of the different assumptions is outside the scope of this paper, we discuss similarities and differences between their results and ours.
These investigations only found one unstable mode.
It is most likely so because the calculations were restricted to a parameter regime where the two modes have not yet been separated from each other, as is the case shown in Fig. \ref{K_Re_sigma_set3} for the lowest $\Ndg$.
These investigations also found that increasing the drag could further destabilize the flow, which is consistent with our interpretation of the Mode 2 instability mechanism.

>>>>

%\documentclass[aps,prl,reprint,twocolumn,superscriptaddress,sort&compress,10pt]{revtex4-1}  % for review and submission
% \documentclass[aps,preprint,12pt]{revtex4-1}  % for review and submission
%\documentclass[aps,twocolumn,floatfix,prl,10pt]{revtex4-1}
%\documentclass[letterpaper,10pt,prl,twocolumn,aps]{revtex4-1}
\documentclass[aps,preprint,floatfix,prl]{revtex4-1}
% \documentclass{jfm}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{color}
\usepackage{longtable}
\usepackage{array}
\usepackage{amssymb}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}

\graphicspath{ {../Paper/images/}{../Paper/images/Growth_Rate_Cont_Plots/} }
\newcommand{\bx}{{\boldsymbol{\hat{x}}}}
\newcommand{\bn}{{\boldsymbol{\hat{n}}}}
\newcommand{\bt}{{\boldsymbol{\hat{t}}}}
\newcommand{\bu}{\mathbf{u}}
\newcommand{\grad}{\mathbf{\nabla}}
\newcommand{\del}{\partial}
\newcommand{\hg}{h_g}
\newcommand{\Rey}{{R}}
\newcommand{\Ndg}{\tilde{N}_g}
\newcommand{\monami}{\textit{monami}}
\newcommand{\ubl}{U_\text{bl}}
\newcommand{\words}[1]{\textbf{(#1)~}}
% \newcommand{\words}[1]{{}}

@@

\definecolor{tableShade}{gray}{0.8}
% \title{\textit{Monami} as an oscillatory hydrodynamic instability in a submerged sea grass bed}
\title{Linear stability analysis for \textit{monami} in a submerged sea grass bed}
% \author{
% Ravi Singh\aff{1}, 
% M. M. Bandi\aff{2},
% Amala Mahadevan\aff{3}
% \and
% Shreyas Mandre\aff{4}}
% \affiliation{
% \aff{1}Department of Physics, Brown University, Providence RI 02912 USA
% \aff{2}OIST Graduate University, Okinawa 904-0495, Japan
% \aff{3}Woods Hole Oceanographic Institution, Woods Hole MA 02543 USA
% \aff{4}School of Engineering, Brown University, Providence RI 02912 USA
% }

\begin{document}
\author{Ravi Singh}
\affiliation{Brown University, Providence RI 02912 USA}
% \author{L. Mahadevan}
% \affiliation{Harvard University, Cambridge MA 02138 USA}
\author{M. M. Bandi}
\affiliation{OIST Graduate University, Okinawa 904-0495, Japan}
\author{Amala Mahadevan}
\affiliation{Woods Hole Oceanographic Institution, Woods Hole MA 02543 USA}
\author{Shreyas Mandre}
\affiliation{Brown University, Providence RI 02912 USA}

@@

% Chen and Jirka (1997), White and Nepf (2007). What are their results and how do they relate to ours? These analyses have investigated instability of hyperbolic tangent profiles using modified versions of Orr Sommerfeld or Rayleigh's equations in the context of shallow water flow instabilities. They have represented the additional drag arising due to vegetation or bottom friction using a parametrization analogous to ours. 
A modified version of the Orr-Sommerfeld equation was analyzed previously \cite{Chu91,Chen97,White07} in the context of instabilities in depth-averaged shallow water flows, where bottom friction replaces or augments vegetation drag.
They assumed the steady profile to be a hyperbolic tangent, the drag to be isotropic, and the flow domain to be infinite in $y$.
One study \cite{White07} also neglected the eddy viscosity in their stability analysis.
While a detailed investigation needed to compare the consequence of the different assumptions is outside the scope of this paper, we discuss similarities and differences between their results and ours.
These investigations only found one unstable mode.
It is most likely so because the calculations were restricted to a parameter regime where the two modes have not yet been separated from each other, as is the case shown in Fig. \ref{K_Re_sigma_set3} for the lowest $\Ndg$.
These investigations also found that increasing the drag could further destabilize the flow, which is consistent with our interpretation of the Mode 2 instability mechanism.
